Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-05-02 Final-Draft.Rmd
edits to tables

---
title: "Investigating the Underprovision of Public Goods: Does Segregation Matter?"
author: "Maria Burzillo"
date: "5/8/2020"
output: 
  pdf_document:
    extra_dependencies: ["rotating"]
bibliography: final_proj_bib.bib
#biblio-style: "apalike"
link_citations: true
header_includes:
  \usepackage{float}
  \usepackage{dcolumn}
  \usepackage{rotating}
  \restylefloat{table}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(gtable)
library(stargazer)
library(tidyverse)
library(gt)
library(gtsummary)
library(knitr)
library(stargazer)
library(lme4)
library(margins)
library(reprex)
library(plm)
library(devtools)
library(lfe)
library(Statamarkdown)
library(readxl)
library(starpolishr)
library(AER)
library(readxl)
library(naniar)
library(mice)
library(gtsummary)
library(VIM)
```

@@

t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
                header = FALSE,
                title = "\\textbf{Racial Polarization in Segregated Cities}",
                single.row = TRUE,
                no.space = FALSE,
                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
                omit.stat = c("ll","rsq"),
                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
                notes = "This table displays...")

# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset. The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project). The original table is displayed for comparison as Figure 1.")

![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 1 in this paper.](table_1.png)

@@

```{r rp_missing_plot, include = FALSE, warning = FALSE}

# don't show the warning, it's just an irrelevant column missing a name

# plot the missing variables if desired

rp_facet <- rp_impute %>%
   select("medincinterp",
             "biggestsplit", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
               "south", "midwest", "west", "whiteideology_fill2", "year")

gg_miss_var(rp_impute, show_pct = TRUE) +
  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")

nrow(rp_impute)

```{r rp_aggr_plot, echo = FALSE}

@@

rp_aggr <- rp_impute %>%
   select("medincinterp",
             "biggestsplit", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
               "south", "midwest", "west", "whiteideology_fill2")

# create an aggr plot for the missing values

aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Racial Polarization Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = .75)

# caption for this plot when I figure out how to do it... : This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial). The plot on the right shows the pattern of missingness among the variables. We can see that approximately 42% of observations are complete (have no missing values). There seems to be a correspondence between missing a value for biggest split and missing biracial. There also seem to be about 2% of values for which most of the variables are missing. However, most observations are not missing more than 2-3 values.

```{r eval = FALSE}
row.plot <- rp_impute %>%
  select(-year.f) %>%
  mutate(id = row_number()) %>%
  gather(-id, key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  ggplot(aes(key, id, fill = isna)) +
    geom_raster(alpha=0.8) +
    scale_fill_manual(name = "",
        values = c('blue', 'red'),
        labels = c("Present", "Missing")) +
    #scale_x_discrete(limits = levels) +
    labs(x = "Variable",
           y = "Observation Number", 
         title = "Missing values in rows") +
    coord_flip() +
  theme_bw()

row.plot

glimpse(rp_impute)
```

```{r eval = FALSE}

row.plot <- fin_imp %>%
  mutate(id = row_number()) %>%
  gather(-id, key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  ggplot(aes(key, id, fill = isna)) +
    geom_raster(alpha=0.8) +
    scale_fill_manual(name = "",
        values = c('blue', 'red'),
        labels = c("Present", "Missing")) +
    #scale_x_discrete(limits = levels) +
    labs(x = "Variable",
           y = "Observation Number", 
         title = "Missing values in rows") +
    coord_flip() +
  theme_bw()

row.plot

@@

```{r fin_aggr_plot, echo = FALSE}

@@

aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = .75)

# this plot tells us that only .58% of the data are complete (not missing anything)

# caption for this plot when I figure out how to do it... : This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data. The plot on the right shows the pattern of missingness among the variables. We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.

@@

@@

# can use the line below to check that there are now no missing values

# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)

@@

```{r fp_imputations_original, include = FALSE}

@@

imp_fs_all <- mice(fin_imp, method = "cart", maxit = 5)

# now there are manyb fewer missing variables!!!

@@

```{r}
#now missing 282261

#before impute:
```

```{r new_imp_less_than_17_nas}

fin_imp <- fin_imp %>%
  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))

fin_imp %>%
  ggplot(aes(x = nas)) +
  geom_histogram()

fin_imp %>%
  group_by(nas) %>%
  summarise(n())

# exclude all observations with 17 out of 22 nas

fin_imp_sub <- fin_imp %>%
  filter(nas < 17)

nrow(fin_imp_sub)

ini <- mice(fin_imp_sub, maxit=0, print=F)

new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)

miss_var_summary(complete(new_imp_fs))

@@

```{r fp_imputations_cities, include = FALSE}

ini <- mice(fin_imp_cities, maxit = 0, print = FALSE)

imp_fs_cities <- mice(fin_imp_cities, method = meth, maxit = 1)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_cities, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

@@

```{r fp_population_full_range}

# what if we condition on population size?

fin_imp_pop_size <- fin_imp %>%
  filter(logpop > 6 & logpop < 16)

nrow(fin_imp_pop_size)

ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)

imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r 95_pop}
fin_imp_pop_trounstine_95 <- fin_imp %>%
  filter(logpop < 11.93437 & logpop > 8.7754)

nrow(fin_imp_pop_trounstine_95)

ini <- mice(fin_imp_pop_trounstine_95, maxit = 0, print = FALSE)

imp_fs_pop_size_trounstine_95 <- mice(fin_imp_pop_trounstine_95, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_first_quartile}

quantile(fin_dge$logpop, c(.25))

quantile(fin_seg$logpop, c(.25), na.rm = T)

fin_imp_pop_trounstine_first_quart <- fin_imp %>%
  filter(logpop < 9.388152)

nrow(fin_imp_pop_trounstine_first_quart)

gg_miss_var(fin_imp_pop_trounstine_first_quart, show_pct = T)

ini <- mice(fin_imp_pop_trounstine_first_quart, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_25 <- mice(fin_imp_pop_trounstine_first_quart, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_25, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_90_trounstine}

quantile(fin_dge$logpop, c(.90))

quantile(fin_seg$logpop, c(.90), na.rm = T)

fin_imp_pop_top_90_trounstine <- fin_imp %>%
  filter(logpop > 11.43575)

fin_seg %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

nrow(fin_imp_pop_top_90_trounstine)

gg_miss_var(fin_imp_pop_top_90_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_top_90_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_top_90_trounstine <- mice(fin_imp_pop_top_90_trounstine, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size_top_90_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_bottom_5_trounstine}

quantile(fin_dge$logpop, c(.05))

quantile(fin_seg$logpop, c(.05), na.rm = T)

fin_imp_pop_bottom_5_trounstine <- fin_imp %>%
  filter(logpop < 8.775581)

fin_seg %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

nrow(fin_imp_pop_bottom_5_trounstine)

gg_miss_var(fin_imp_pop_bottom_5_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_bottom_5_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_5_trounstine <- mice(fin_imp_pop_bottom_5_trounstine, method = meth, maxit = 1)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_5_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_pop_size_bottom_5_trounstine))

miss_var_summary(fin_imp_cities)

nrow(complete(imp_fs_pop_size_bottom_5_trounstine))

5039 - 4966

```{r population_bottom_1}

quantile(fin_dge$logpop, c(.01))

quantile(fin_seg$logpop, c(.20), na.rm = T)

fin_imp_pop_bottom_1_trounstine <- fin_imp %>%
  filter(logpop < 8.364976 )

fin_seg %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

nrow(fin_imp_pop_bottom_1_trounstine)

gg_miss_var(fin_imp_pop_bottom_1_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_bottom_1_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_1_trounstine <- mice(fin_imp_pop_bottom_1_trounstine, method = meth, maxit = 1)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_over_Baqir}

# Baqir et al uses city as population above 25,000

baqir <- log(25000)

fin_imp_pop_over_baqir <- fin_imp %>%
  filter(logpop > baqir )

nrow(fin_imp_pop_over_baqir)

gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)

ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)

imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_under_Baqir}

# Baqir et al uses city as population above 25,000

baqir <- log(25000)

fin_imp_pop_under_baqir <- fin_imp %>%
  filter(logpop < baqir )

nrow(fin_imp_pop_under_baqir)

gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)

ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)

imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_mid_50}

# essentially the same - let's do full population
(quantile(fin_seg$logpop, c(.25, .75), na.rm = T))
(quantile(fin_imp$logpop, c(.25, .75), na.rm = T))

baqir <- log(25000)

fin_imp_pop_mid_50 <- fin_imp %>%
  filter(logpop > 5.777652 & logpop < 7.936303)

nrow(fin_imp_pop_mid_50)

gg_miss_var(fin_imp_pop_mid_50, show_pct = T)

ini <- mice(fin_imp_pop_mid_50, maxit = 0, print = FALSE)

imp_fs_pop_mid_50 <- mice(fin_imp_pop_mid_50, method = meth, maxit = 1)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_mid_50, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_1_trounstine}

(quantile(fin_seg$logpop, c(.99), na.rm = T))
(quantile(fin_dge$logpop, c(.99), na.rm = T))

fin_imp_top_1_trounstine <- fin_imp %>%
  filter(logpop > 13.1907 )

nrow(fin_imp_top_1_trounstine)

gg_miss_var(fin_imp_top_1_trounstine, show_pct = T)

ini <- mice(fin_imp_top_1_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_top_1_trounstine <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_top_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

nrow(complete(imp_fs_pop_top_1_trounstine))

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_1}

(quantile(fin_seg$logpop, c(.99), na.rm = T))
(quantile(fin_dge$logpop, c(.99), na.rm = T))

fin_imp_top_1 <- fin_imp %>%
  filter(logpop > 11.28648)

nrow(fin_imp_top_1)

gg_miss_var(fin_imp_top_1, show_pct = T)

ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)

imp_fs_pop_top_1 <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

nrow(complete(imp_fs_pop_top_1))

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected. First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables. Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots. All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well. The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region). However, this is more or less to be expected given the small number of imputations performed in these cases. Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern. See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables. The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.

densityplot(imp_1_rp)

```{r rp_imp_plot, include = FALSE}

```{r rp_stripplot, include = FALSE}

# this looks good? All reasonable values...

stripplot(imp_1_rp, biggestsplit)

```{r fs_densityplot, echo = FALSE}

densityplot(imp_fs)
densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
       chng5pctlatino + chng5pctasian + ideology_fill)

```{r fs_imp_plot, include = FALSE}

```{r fs_stripplot, include = FALSE}

# this looks good? All reasonable values...

Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters. The results for the analyses using the racial polarization dataset are presented in tables 1-3.

@@

imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_1_rp_sum_table)

@@

imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_2_rp_sum_table)

@@

imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_3_rp_sum_table)

@@

For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each. The pooled results are presented in tables 4-6.

# FS data results

```{r fs_imputed_pooled_regressions, include = FALSE}
# Main Analysis 2: Imputations

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

# fit multiple imputed datasets

fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm2 <- pool(fit_imp_felm2)
imp_felm2_sum <- summary(pool_imp_felm2)

fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm3 <- pool(fit_imp_felm3)
imp_felm3_sum <- summary(pool_imp_felm3)

>>>>

---
title: "Investigating the Underprovision of Public Goods: Does Segregation Matter?"
author: "Maria Burzillo"
date: "5/8/2020"
output: 
  pdf_document:
    fig_caption: true
bibliography: final_proj_bib.bib
#biblio-style: "apalike"
link_citations: true
header_includes: 
  \usepackage{float}
  \usepackage{multirow}

@@

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(stargazer)
library(tidyverse)
library(gtsummary)
library(knitr)
library(AER)
library(lme4)
library(margins)
library(lfe)
library(readxl)
library(mice)
library(VIM)
library(kableExtra)
```

@@

@@

```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial). The plot on the right shows the pattern of missingness among the variables. We can see that approximately 42\\% of observations are complete (have no missing values). There seems to be a correspondence between missing a value for biggest split and missing biracial. There also seem to be about 2\\% of values for which most of the variables are missing. However, most observations are not missing more than 2-3 values.", fig.width= 6, fig.height = 5, warning = F, fig.pos="H"}

@@

rp_aggr <- rp_impute %>%
   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
            "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
               "south", "midwest", "west") %>%
  rename("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, 
         "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp,
         "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp, 
         "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,
         "% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp,
         "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,
         "West" = "west")

# create an aggr plot for the missing values
par(font = 1)
aggr(rp_aggr, bars = TRUE,  col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", line = 3, oma = c(1,3,5,1), cex.axis = .5, font.main = 1, font.axis = 1, cex.main = 1, cex.lab = .75)

@@

```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data. The plot on the right shows the pattern of missingness among the variables. We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}

@@

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
# this plot tells us that only .58% of the data are complete (not missing anything)

@@

rp_impute_labels <- rp_impute

rp_impute_labels$biggestsplit <- "Racial Divide"
rp_impute_labels$medincinterp <- "Median HH Income"

#c("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp, "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp,  "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,"% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp, "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,"West" = "west")

@@

@@

```{r fp_imputations_original, eval = FALSE, include = FALSE}

@@

# now there are many fewer missing variables!!!

@@

Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected. First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables. Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots. All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well. The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region). However, this is more or less to be expected given the small number of imputations performed in these cases. Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern. See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables. The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.

my.settings <- list(
  par.main.text = list(font = 1)
)

densityplot(imp_1_rp, main = "Density Plots of Imputed and Original Data by Variable\nin the Racial Polarization Dataset",
      par.settings = my.settings,
      par.strip.text = list(cex = .7))

@@

```{r fs_densityplot, echo = FALSE, eval = FALSE}

densityplot(imp_fs)
densityplot(x = imp_fs , data = ~ H_citytract_NHW_i + chng5pctblk + 
       chng5pctlatino + chng5pctasian + ideology_fill)

@@

Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters. The results for the analyses using the racial polarization dataset are presented in tables X1-X3.

@@

imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum) %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_1_rp_sum_table)

@@

imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum) %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_2_rp_sum_table)

@@

imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum) %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_3_rp_sum_table)

@@

\newpage
